\font\huge=cmr16 at 24pt
\font\sc=cmcsc10 at 10pt

\def\indent{\hskip2em}
\def\vsep{\vskip1.5em\vfil}

\vsize=8.5in
\voffset=-0.25in

\setbox0=\vbox{
  \hbox to \hsize {\huge \hfill Jakub Daniel \hfill}
  \vsep
  \hbox to \hsize {\hfill Curriculum Vitae \hfill}
}

\output={%
  \setbox255=\vbox{%
    \vbox to 0.625in {%
      \unvbox0%
    }%
    \vsep%
    \hrule%
      \vsep%
      \vbox to \vsize {\unvbox255\vfil}%
      \vsep%
    \hrule%
    \vsep%
    \hfil\the\pageno\hfil%
    \global\advance\pageno1%
  }%
  \shipout\box255%
}

%\vbox{
%  \halign{%
%    \indent \hbox to 8em{#\hfil}&#\hfil\cr
%    \multispan2{\bf Personal} \hfil\cr
%    \cr
%
%    Date of Birth:  & 2 July 1989\cr
%    Place of Birth: & Brand\'ys nad Labem, Czech Republic\cr
%    Residence:      & Prague, Czech Republic\cr
%    Nationality:    & Czech\cr
%    Languages:      & Czech (native), English (FCE awarded in 2007)\cr
%  }
%}
%\vsep
\vbox{
  \halign{%
    \indent \hbox to 8em{#\hfil}&#\hfil\cr
    \multispan2{\bf Contact} \hfil\cr
    \cr

    Address: & Department of Distributed and Dependable Systems \cr
             & Faculty of Mathematics and Physics \cr
             & Charles Univesity in Prague \cr
             %& Malostransk\'e n\'am\v{e}st\'{\i} 25, 118 00 Prague 1, Czech Republic \cr
             & Malostranske namesti 25, 118 00 Prague 1, Czech Republic \cr
    \cr

    E-Mail:  & {\tt daniel@d3s.mff.cuni.cz} \cr
    WWW:     & {\tt http://d3s.mff.cuni.cz/\~{ }daniel} \cr
  }
}
\vsep
\vbox{
  \halign{%
    \indent #\hfil\cr
    \multispan1{\bf Education} \cr
    \cr

    PhD studies in Computer Science since 2013 \cr
    Faculty of Mathematics and Physics, Charles University in Prague\cr
    topic: Program Verification Using Abstraction and Logics\cr
    \cr

    Mgr. (MSc equivalent) in Computer Science 2011--2013 \cr
    %RNDr. (MSc extension) in Computer Science 2016 \cr
    Faculty of Mathematics and Physics, Charles University in Prague \cr
    thesis: Analysis of Interface Automata with On-Demand Replication\cr
    \cr

    Bc. in Computer Science 2008--2011 \cr
    Faculty of Mathematics and Physics, Charles University in Prague \cr
  }
}
\vsep
\vbox{
  \halign{%
    \indent #\hfil\cr
    \multispan1{\bf Software} \cr
    \cr
    {\sc Bacon}: Behaviour Abstraction for Containers \hfil\cr
    {\tt https://github.com/d3sformal/bacon.git} \cr
    \cr
    {\sc Panda}: Predicate Abstraction in Dynamic Analysis \hfil\cr
    Started as Google Summer of Code project in 2013 \cr
    {\tt https://github.com/d3sformal/panda.git} \cr
  }
}
\vsep
{
  \newcount\pubnum
  \pubnum=0
  \def\item{\cr\global\advance\pubnum by 1[\the\pubnum] &}
  \vbox{
    \halign{%
      \indent {\hsize=4em #\hfil}\hskip1em&{\advance\hsize by -7em \vtop{\parindent=0pt #}\hfil} \cr
      \multispan2{\bf Publications} \hfil\cr

      \item J. Daniel, A. Cimatti, A. Griggio, S. Tonetta, and S. Mover. Infinite-state Liveness-to-Safety via Implicit Abstraction and Well-founded Relations. Accepted for publication in Proceedings of CAV 2016. \cr

      \item J. Daniel and P. Parizek. {\sc Panda}: Simultaneous Predicate Abstraction and Concrete Execution. In Proceedings of the 11th Haifa Verification Conference, LNCS, vol. 9434, Nov 2015. \cr

      \item T. Ball and J. Daniel. Deconstructing Dynamic Symbolic Execution. In Proceedings of the 2014 Marktoberdorf Summer School on Dependable Software Systems Engineering, IOS Press, Jan 2015. \cr

      %\item J. Daniel and P. Par\'{\i}zek. Predicate Abstraction in Program Verification: Survey and Current Trends. Accepted for publication in Proceedings of ICCSW 2014 \cr
      \item J. Daniel and P. Parizek. Predicate Abstraction in Program Verification: Survey and Current Trends. In Proceedings of 2014 Imperial College Computing Student Workshop, OASIcs, vol. 43. \cr

      %\item J. Daniel, P. Par\'{\i}zek, and C. P\u{a}s\u{a}reanu. Predicate Abstraction in Java Pathfinder. In Proceedings of the Java Pathfinder Workshop 2013, ACM SIGSOFT Software Engineering Notes, 39(1) \cr
      \item J. Daniel, P. Parizek, and C. Pasareanu. Predicate Abstraction in Java Pathfinder. In Proceedings of the Java Pathfinder Workshop 2013, ACM SIGSOFT Software Engineering Notes, 39(1) \cr
      % Garbage item. Nothing to do with me!
      %\item T. Knap, J. Michelfeit, J. Daniel, P. Jerman, D. Rychnovsk\'{y}, T. Soukup, and M. Ne\v{c}ask\'{y}. ODCleanStore: A Framework for Managing and Providing Integrated Linded Data on the Web. In Proceedings of WISE 2012, LNCS, vol. 7651, Nov 2012.\cr
      %\item T. Knap, J. Michelfeit, J. Daniel, P. Jerman, D. Rychnovsky, T. Soukup, and M. Necasky. ODCleanStore: A Framework for Managing and Providing Integrated Linded Data on the Web. In Proceedings of WISE 2012, LNCS, vol. 7651, Nov 2012.\cr
    }
  }
}
\vsep
\vbox{
  \halign to \hsize {%
    \indent {\hsize=5em #\hfil}&{\hsize=5em #\hfil}\hskip1em& {#}\hskip1em& {#}\hfil \cr
    \multispan3{\bf Teaching Experience} \hfil\cr
    \cr

    Summer & '14, '15 & System Behaviour Models and Verification   & Charles University in Prague\cr
    %Winter & '13, '14 & Developing Applications for Mobile Devices & Charles University in Prague\cr
    Winter & '14      & Java                                       & Charles University in Prague\cr
  }
}
\vsep
\vbox{
  \halign{%
    \indent \hbox to \hsize{#\hfil}&#\hfil\cr
    \multispan1{\bf Languages} \hfil\cr
    \cr
    Czech (native), English (FCE awarded in 2007) \cr
  }
}

\bye
